Fractional anisotropy as a tracer of cosmic voids

### 2014-12-11 cosmic_voids.tex
Correction of labels for fractional anisotropy profiles

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes over a slide of the simulation. Some important points can be 
concluded from this figure (these results are consistent with those of 
\citet{Libeskind13}).

@@

From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
tracer of voids as is almost perfectly correlated with low values of 
$\lambda_1$. Then, it reaches a maximum value, namely sheets and filaments, 
for finally reaching knots, which feature low FA values. This behaviour can 
be thought as a sort of one-dimensional tomography of the Cosmic Web. This
characteristic allows us to propose an optimal threshold value for both 
web schemes where the FA is maximized. Specifically we propose a value of 
$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
above these values, voids would span over very anisotropic regions, which 
must correspond to sheets and filaments. A threshold below would imply 
very low volume filling fractions of voids and dominant sheets. Finally, 
the density field do not correlate well with $\lambda_1$ (as calculated 
for both web schemes). Moreover, due to its monotonic increase, an estimate 
of an optimal threshold is not as clear as for the FA.

Once set the optimal thresholds for the web schemes, we proceed in Fig. 
\ref{fig:FAShapeness} to sample the FA along with the prolatenes for a 
random sample of cells classified into the four environments. Then, we 
associate a spheroidal geometry with different ranges of these properties
in order to illustrate the underlying local dynamics of the sampled cells.

From this figure we conclude that sheets displays, as expected, very 
anisotropic distributions, namely above $FA=0.95$. They are also biased 
towards oblate geometries, however there are some elongated sheets as 
well. Filaments are not as anisotropic as sheets, ranging from middle up 
to high FA values. They exhibit prolate geometries, but a considerable 
amount of them are biased towards slightly more oblate values. Voids and 
knots are the only environments featuring with low FA values, thus 
indicating very isotropic expanding/collapsing dynamics at their centres. 
However, voids span over a very wide range of FA and geometries, whereas 
knots only span over low to middle FA values and display a biased oblate 
geometry.

@@

@@

  \captionof{figure}{\small }

@@

  \captionof{figure}{\small Volume functions of voids catalogued by each 
  used scheme. Left panel (watershed transform over the FA field of the T-web 
  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
  (over the density field). Gray curves correspond to voids without boundary 
  removal whereas black curves are associated to voids merged through boundary 
  removal process. Dotted lines correspond to original continuous fields, 
  while segmented lines correspond to fields with a 1st-order median filtering 
  and continuous lines to a 2nd-order median filtering.}

@@

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG1.pdf}

@@

%.........................................................................
%FIGURE 6: Velocity profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG1.pdf}

  \captionof{figure}{\small Velocity of voids for each finding scheme.}

%.........................................................................
%FIGURE 1: Volume Filling Fractions for environs
%\begin{flushleft}
%\begin{figure*}
%\centering
%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}  
%  
%  \captionof{figure}{\small Volume Filling Fraction for each type of 
%  environment with respect to the chosen threshold $\lambda_{th}$ for both
%  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
%  threshold value is chosen such that the fractional anisotropy along the 
%  void-sheet boundaries has a median value of $FA=0.95$.}
%
%  \label{fig:VFF}
%  \vspace{0.1 cm}
%
%\end{figure*}
%\end{flushleft}
%.........................................................................

%.........................................................................
%%FIGURE 4: density field,impression
%\begin{figure*}
%\centering

%  \includegraphics[trim = 16mm 10mm 295mm 12mm, clip, keepaspectratio=true,
%  width=0.27\textheight]{./figures/cosmicweb_density.pdf}  
%  \captionof{figure}{\small }

%  \label{fig:density_field}
%\end{figure*}
%.........................................................................

>>>>

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes over a slide of the simulation. Some important points can be 
concluded from this figure:

@@

From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
tracer of voids as is almost perfectly correlated with low values of 
$\lambda_1$. Then, it reaches a maximum value, namely sheets and filaments, 
for finally reaching knots, which feature low FA values. This behaviour can 
be thought as a sort of one-dimensional tomography of the Cosmic Web. This
characteristic allows us to propose an optimal threshold value for both 
web schemes where the FA is maximized. Specifically we propose a value of 
$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
above these values, voids would span over very anisotropic regions, which 
must correspond to sheets and filaments. A threshold below would imply 
very low volume filling fractions of voids and dominant sheets. Finally, 
the density field do not correlate well with $\lambda_1$ (as calculated 
for both web schemes), and due to its monotonic increase, an estimate of 
an optimal threshold is not as clear as for the FA.

Once set the optimal thresholds for the web schemes, we proceed in Fig. 
\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
sample of cells previously classified into one of the four environments. 
The prolateness is introduced here for differentiating sheets and filaments
featuring high FA values. In order to illustrate the underlying local 
dynamics sampled by the cells, we also sketch different spheroidal 
geometries according to the relative strength of each eigenvalue, and 
then, we associate them to different ranges of the FA and the prolateness. 
From this, we conclude sheets display very anisotropic distributions, 
namely above $FA=0.95$. They are also biased towards oblate geometries, 
however there are some elongated sheets as well. Filaments are not as 
anisotropic as sheets, ranging from middle up to high FA values. They 
exhibit prolate geometries, but a considerable fraction of them are biased 
towards slightly more oblate values. Voids and knots are the only 
environments featuring with low FA values, thus indicating very isotropic 
expanding/collapsing dynamics at their centres. However, voids span over 
a very wide range of FA and geometries, whereas knots only span over low 
to middle FA values and display a biased oblate geometry.

@@

\[ \mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr \]

\[ \mathcal{C} < 1 \]

\[ \mathcal{C} > 1 \]

@@

  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
  random sample of cells (left panel) and for different spherical 
  geometries (right panel). For the cells, each environment is coded with
  a different colour, i.e. voids corresponds with dark blue points, 
  sheets with green, filaments with orange and knots with cyan. The axis 
  of the spheroids are computed from the relative strengths of the 
  eigenvalues, so their shape sketch the relative expanding/collapsing 
  dynamics into each direction.}

@@

  \captionof{figure}{\small Volume functions of voids for both built 
  catalogues. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

@@

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_VwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG1.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_VwebFAG1.pdf}

@@
